%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}



% --- code font ---
\usepackage{courier}
\newcommand{\code}[1]{{\fontfamily{pcr}\selectfont #1}}
% ---------- Publications helpers (CV) ----------
\newcommand{\pubdoi}[1]{\href{https://doi.org/#1}{doi:\allowbreak #1}}
\newcommand{\pubtitle}[1]{``#1.''}
\newcommand{\pubjournal}[3]{\textit{#1}, \textbf{#2}, #3}
% ---------------------------------------------
%
% --- Conferences/Workshops: title-only first line, details on following lines ---
\newcommand{\cvEvent}[4]{%
  \item \textbf{#1}\\[-2pt]
  \textit{\small #2} \hfill \textit{\small #3}\\[-2pt]
  \textit{\small #4}\vspace{2pt}
}
%
% ---------- Software/Data helpers (CV) ----------
\newcommand{\softlink}[2]{\href{#1}{#2}}
\newcommand{\softrepo}[3]{\textit{#1}. \softlink{#2}{#2} #3}
% Usage: \softrepo{<Project>}{<URL>}{<optional: ; \pubdoi{...} ; vX.Y ; etc.>}
% ----------------------------------------------
\usepackage{academicons}
%



%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}


% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

%
% After ALL margin/textwidth adjustments:
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\setlength{\headwidth}{\textwidth}  % <-- key line
\cfoot{\small \thepage}
%


\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Ruo-Yu Guan} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:8618604511940}{+86 186 0451 1940}
    $|$
    \faAt \hspace{.5pt} \href{mailto:ruoyuguan.physics@gmail.com}{ruoyuguan.physics@gmail.com}
    $|$
    \faGlobe \hspace{.5pt} \href{https://ruoyuguan.github.io/}{Portfolio}
    $|$
    \faMapMarker \hspace{.5pt} \href{https://www.google.com/maps/place/Huazhong+University+of+Science+and+Technology/@30.5138311,114.4097043,15z/data=!4m6!3m5!1s0x342ea4a4f8a230e9:0xf42f097ec953d0b1!8m2!3d30.5130043!4d114.4202756!16zL20vMDQ4bjRt?entry=ttu&g_ep=EgoyMDI2MDEyOC4wIKXMDSoASAFQAw%3D%3D}{Wuhan, China}
    \\ \vspace{3pt}
\faExternalLink \hspace{.5pt} \href{https://orcid.org/0009-0000-8680-1762}{ORCID}
$|$
\faGraduationCap \hspace{.5pt} \href{https://scholar.google.com/citations?user=krWheg0AAAAJ&hl=en}{Google Scholar}
$|$
\faSearch \hspace{.5pt} \href{https://ui.adsabs.harvard.edu/search/q=orcid%3A0009-0000-8680-1762}{ADS}
\end{center}%\faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/ruoyu-guan-physics/}{LinkedIn}
%\faGithub \hspace{.5pt} \href{https://github.com/ruoyuguan}{GitHub}


\section{Research Profile}
  \vspace{3pt}
\resumeItemListStart
\resumeItem{Gamma-ray burst astrophysics (prompt emission, polarization modeling, time-series analysis).}
\resumeItem{Multiwavelength data analysis (Chandra X-ray observations and Gaia astrometric cross-matches).}
\resumeItem{Compact stellar binaries (double white dwarfs) and Galactic structure inference via population synthesis and Bayesian methods (LISA/TianQin).}
\resumeItemListEnd

%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeEducationHeading
      {Huazhong University of Science and Technology (HUST)}{Wuhan, China}{School of Physics; National Gravitation Laboratory}{Sep.\ 2025 \textbf{--} Jun.\ 2029 \footnotesize{\textit{(expected)}}}
      {Ph.D. in Physics (Theoretical Physics) \textit{(in progress)}}{Supervisor: Prof.\ Yan Wang}%\href{https://faculty.hust.edu.cn/wangyan11/en/index.htm}{\color{blue}Prof.\ Yan Wang}
    \resumeItemListStart
      \resumeItem{Research focus: gravitational-wave astrophysics (galactic double white dwarfs).}
    \resumeItemListEnd

    \resumeEducationHeading
      {The University of Hong Kong (HKU)}{Hong Kong SAR, China}{Department of Physics, Faculty of Science}{Sep.\ 2023 \textbf{--} Jul.\ 2024; degree conferred Nov.\ 2024}
      {M.Sc. in Physics}{Supervisor: Assoc.\ Prof.\ Stephen Chi-Yung Ng}%\href{https://astro.physics.hku.hk/~ncy/}{\color{blue}Assoc. Prof.\ Stephen Chi-Yung Ng}
    \resumeItemListStart
      \resumeItem{Capstone project: \textit{Identifying Sources in Cygnus OB2 Using Multiwavelength Observations}.}
    \resumeItemListEnd

    \resumeEducationHeading
      {Jilin University (JLU)}{Changchun, China}{Department of Materials Science, School of Materials Science and Engineering}{Sep.\ 2018 \textbf{--} Jun.\ 2022}
      {B.Sc. in Materials Physics}{}
    \resumeItemListStart
      \resumeItem{Graduation thesis: \textit{Study on the Prompt Emission of Gamma-ray Bursts and its Polarization}.}
      \resumeItem{Research mentor: Prof.\ Mi-Xiang Lan (Center for Theoretical Physics \& College of Physics, Jilin University).}%\href{https://theory.jlu.edu.cn/info/1042/1053.htm}{\color{blue}Prof.\ Mi-Xiang Lan}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%---------------------------------%


%----------- RESEARCH POSITIONS -----------

\section{Research Positions}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Huazhong University of Science and Technology}{Wuhan, China}
      {Research Assistant (contract), Department of Astronomy}{Nov.\ 2024 \textbf{--} Jun.\ 2025}
    \resumeItemListStart
      \resumeItem{Supervisor: Prof.\ Yuan-Chuan Zou.}
      \resumeItem{Gamma-ray burst (GRB) research (see Research Experience / Publications).}
      % \resumeItem{(Optional) Supported by National SKA Program of China (Grant No.\ 2022SKA0130100).}
    \resumeItemListEnd

  \resumeSubHeadingListEnd






%----------- PUBLICATIONS -----------

\section{Publications}
  \vspace{2pt}

  \textbf{Refereed journal articles}
  \vspace{-2pt}
  \begin{enumerate}[leftmargin=0.15in, label={[\arabic*]}, itemsep=0pt, topsep=3pt]%label={[J\arabic*]}
    \item \textbf{Ruo-Yu Guan} and Mi-Xiang Lan.
      \pubtitle{Interpreting time-integrated polarization data of gamma-ray burst prompt emission}
      \pubjournal{Astronomy \& Astrophysics}{670}{A160 (2023)}.
      \pubdoi{10.1051/0004-6361/202243805}.

    \item \textbf{Ruo-Yu Guan}, Fei-Fei Wang, and Yuan-Chuan Zou.
      \pubtitle{Hurst index of gamma-ray burst light curves and its statistical study}
      \pubjournal{Journal of High Energy Astrophysics}{51}{100559 (2026)}.
      \pubdoi{10.1016/j.jheap.2026.100559}.
  \end{enumerate}

  % \vspace{4pt}
  % \textbf{Software / data releases}
  % \vspace{-2pt}
  % \begin{enumerate}[leftmargin=0.15in, label={[\arabic*]}, itemsep=0pt, topsep=3pt]
  %   % (Optional; add to preamble once)
  %   % ---------- Software/Data helpers (CV) ----------
  %   % \newcommand{\publink}[2]{\href{#1}{#2}}
  %   % \newcommand{\pubrepo}[2]{\textit{#1}. \publink{#2}{#2}}
  %   % ----------------------------------------------
  %   \item \textbf{Ruo-Yu Guan}. \textit{<Project Name>}. \href{<URL>}{<URL>}. % optional: \pubdoi{10.5281/zenodo.XXXXXXX}.
  % \end{enumerate}

  % \vspace{4pt}
  % \textbf{Preprints}
  % \vspace{-2pt}
  % \begin{enumerate}[leftmargin=0.15in, label={[\arabic*]}, itemsep=0pt, topsep=3pt]
  %   \item ...
  % \end{enumerate}

  % \vspace{4pt}
  % \textbf{Submitted manuscripts}
  % \vspace{-2pt}
  % \begin{enumerate}[leftmargin=0.15in, label={[\arabic*]}, itemsep=0pt, topsep=3pt]
  %   \item ...
  % \end{enumerate}

  % \vspace{4pt}
  % \textbf{Manuscripts in preparation}
  % \vspace{-2pt}
  % \begin{enumerate}[leftmargin=0.15in, label={[\arabic*]}, itemsep=0pt, topsep=3pt]
  %   \item ...
  % \end{enumerate}

  % \vspace{4pt}
  % \textbf{Conference proceedings / non-refereed}
  % \vspace{-2pt}
  % \begin{enumerate}[leftmargin=0.15in, label={[\arabic*]}, itemsep=0pt, topsep=3pt]
  %   \item ...
  % \end{enumerate}

  %----------------------------------%

%----------- RESEARCH EXPERIENCE -----------

\section{Research Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \item
      \textbf{Milky Way Structure Inference from Multi-Messenger Observations of Double White Dwarf (DWD) Binaries}\\[-2pt]
      \textit{National Gravitation Laboratory and School of Physics, HUST} \hfill \textit{Wuhan, China}\\[-2pt]
      \textit{Ph.D.\ research (Supervisor: Prof.\ Yan Wang)} \hfill \textit{Jul.\ 2025 \textbf{--} Present}
      \resumeItemListStart
        \resumeItem{Research focus: gravitational-wave (GW) astrophysics and Milky Way structure inference using Galactic double white dwarf (DWD) binaries as multi-messenger targets.}
        \resumeItem{Building a simulation-based inference pipeline integrating population synthesis (\code{COSMIC}) with hierarchical Bayesian inference (e.g., \code{GWpopulation}).}
        \resumeItem{Quantifying selection effects, detector response, and observational uncertainties for space-based GW observations (Laser Interferometer Space Antenna (LISA) / TianQin context).}
        \resumeItem{\textbf{Milestone:} Ph.D.\ proposal approved; proposal title: \textit{Milky Way Structure Inference from Multi-Messenger Observations of Double White Dwarf Binaries}.}
        % \resumeItem{(Optional) Update the proposal title once an official filed English title is available.}
      \resumeItemListEnd
      \vspace{2pt}

    \item
      \textbf{Time-Series and Correlation Analysis of Gamma-Ray Burst (GRB) Light Curves}\\[-2pt]
      \textit{Department of Astronomy, HUST} \hfill \textit{Wuhan, China}\\[-2pt]
      \textit{Pre-Ph.D.\ research (Research Assistant, contract; Supervisor: Prof.\ Yuan-Chuan Zou)} \hfill \textit{Oct.\ 2024 \textbf{--} Jan.\ 2026}
      \resumeItemListStart
        \resumeItem{Conducted GRB light-curve time-series analysis using detrended fluctuation analysis (DFA) and Hurst exponent estimation; performed statistical correlation studies in \code{Python}.}
        \resumeItem{Maintained \code{Python}-based workflows for preprocessing, feature extraction, statistical analysis, and visualization; supported manuscript preparation.}
        \resumeItem{Resulted in a first-author refereed journal article (see Publications).}
        \resumeItem{Supported by the National SKA Program of China (Grant No.\ 2022SKA0130100).}
      \resumeItemListEnd
      \vspace{2pt}

    \item
      \textbf{Identifying Sources in Cygnus OB2 Using Multiwavelength Observations}\\[-2pt]
      \textit{Department of Physics, Faculty of Science, HKU} \hfill \textit{Hong Kong SAR, China}\\[-2pt]
      \textit{M.Sc.\ capstone project (Supervisor: Assoc.\ Prof.\ Stephen Chi-Yung Ng)} \hfill \textit{Sep.\ 2023 \textbf{--} Jun.\ 2024}
      \resumeItemListStart
        \resumeItem{Reduced and analyzed \textit{Chandra} X-ray observations using standard pipelines with the Chandra Interactive Analysis of Observations (CIAO) software, including source detection and quality control.}
        \resumeItem{Merged 18 X-ray observations in the Cygnus OB2 region and assembled a catalog of detected X-ray sources.}
        \resumeItem{Cross-matched X-ray sources with \textit{Gaia} counterparts to classify association members versus foreground/background objects.}
      \resumeItemListEnd
      \vspace{2pt}

    \item
      \textbf{Gamma-Ray Burst Prompt Emission and Polarization}\\[-2pt]
      \textit{Center for Theoretical Physics and College of Physics, JLU} \hfill \textit{Changchun, China}\\[-2pt]
      \textit{Undergraduate research (Mentor: Prof.\ Mi-Xiang Lan)} \hfill \textit{2022 \textbf{--} Feb.\ 2023}
      \resumeItemListStart
        \resumeItem{Collected and organized GRB prompt-emission spectral parameters and polarization measurements from the literature by instrument and energy band.}
        \resumeItem{Computed time-integrated polarization degrees for $\sim$37 GRBs under a synchrotron-emission framework using \code{IDL}; filtered unphysical solutions and compared model predictions with observations.}
        \resumeItem{Resulted in a first-author refereed journal article (see Publications).}
        \resumeItem{Supported by the National Natural Science Foundation of China (Grants No.\ 11903014 and 12147217).}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
%------------------------------------------%

%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{

        \textbf{Languages:}{ Chinese (Mandarin: native; Cantonese: conversational); English (IELTS 6.5, 2023; completed an English-taught M.Sc. at HKU).} \\ \vspace{3pt}%English (professional proficiency; completed an English-taught M.Sc. at HKU)

        \textbf{Programming:}{ \textbf{\code{Python}} (primary); \code{MATLAB}, \code{Mathematica}, \code{R} (familiar); \code{IDL}, \code{C++} (prior experience).} \\ \vspace{3pt}

        \textbf{Methods:}{ time-series analysis; statistical correlation analysis; hierarchical Bayesian inference (\code{GWpopulation}; Markov chain Monte Carlo (MCMC)); Monte Carlo simulation and mock-catalog generation.} \\ \vspace{3pt}

        \textbf{Scientific computing:}{ \code{NumPy}, \code{SciPy}, \code{Pandas}, \code{Matplotlib}; \code{Jupyter}; Flexible Image Transport System (FITS) data handling; pipeline automation (bash/Python scripts).} \\ \vspace{3pt}

        \textbf{Astrophysics \& gravitational-wave (GW):}{ population synthesis (\code{COSMIC}); gravitational-wave population inference; catalog-based population studies.} \\ \vspace{3pt}

        \textbf{Scholarly writing:}{ \LaTeX; \code{Bib\TeX}.} \\ \vspace{3pt}

        \textbf{Computing environment:}{ \code{Git}/\code{GitHub}; \code{bash} (shell scripting); Windows, macOS, Linux (Ubuntu); high-performance computing (HPC) (remote Linux servers; batch jobs); Secure Shell (SSH)-based workflows.} \\

    }}
  \resumeSubHeadingListEnd
%-------------------------------------------

%----------- SOFTWARE & DATA RELEASES -----------

% \section{Software \& Data Releases}
%   \vspace{2pt}
%   \textbf{Open-source software}
%   \vspace{-2pt}
%   \begin{enumerate}[leftmargin=0.15in, label={[\arabic*]}, itemsep=0pt, topsep=3pt]
%     % \item \textbf{Ruo-Yu Guan}. 
%     %   \softrepo{<Repository / package name>}{<URL>}{; v<version> (release date); \pubdoi{10.5281/zenodo.XXXXXXX}.}
%     %   \\
%     %   \textit{\small Brief descriptor: purpose, methods, datasets, or reproducibility notes.}
%   \end{enumerate}
%
%   \vspace{4pt}
%   \textbf{Datasets / catalogs}
%   \vspace{-2pt}
%   \begin{enumerate}[leftmargin=0.15in, label={[\arabic*]}, itemsep=0pt, topsep=3pt]
%     % \item \textbf{Ruo-Yu Guan}. 
%     %   \softrepo{<Dataset / catalog title>}{<URL or DOI landing page>}{; \pubdoi{10.5281/zenodo.XXXXXXX}.}
%     %   \\
%     %   \textit{\small Brief descriptor: scope, format (e.g., FITS/CSV), access conditions.}
%   \end{enumerate}
%
%-----------------------------------------------%


%----------- TALKS & PRESENTATIONS -----------

\section{Talks \& Presentations}
  \vspace{2pt}
  \resumeSubHeadingListStart

    \item \small{
      \textbf{2024 PKU International PhD Student Forum on the Frontiers of Modern Astronomy}\\[-2pt]
      \textit{Poster presentation: ``Time-integrated Polarizations of Gamma-ray Burst Prompt Phase''} \hfill \textit{Dec.\ 2024}\\[-2pt]
      \textit{Kavli Institute for Astronomy and Astrophysics, Peking University}
    }

  \resumeSubHeadingListEnd
%------------------------------------------


%----------- CONFERENCES & WORKSHOPS -----------

\section{Conferences \& Workshops}
  \vspace{2pt}
  \resumeSubHeadingListStart

    \cvEvent
      {2025 Gravitational Wave Data Analysis Summer School}
      {Participant}
      {Aug.\ 2025}
      {Lanzhou Center for Theoretical Physics}

    \cvEvent
      {The First Edinburgh School for Extragalactic Astronomy (ESEA-I)}
      {Participant}
      {Jun.\ 2025}
      {Institute for Astronomy, The University of Edinburgh}

    \cvEvent
      {Gravitational Wave Open Data Workshop 2025}
      {Participant}
      {May 2025}
      {Gravitational Wave Open Science Center (GWOSC)}

    \cvEvent
      {2024 PKU International PhD Student Forum on the Frontiers of Modern Astronomy}
      {Poster presenter}
      {Dec.\ 2024}
      {Kavli Institute for Astronomy and Astrophysics, Peking University}

    \cvEvent
      {International Conference on Space Sustainability 2024}
      {Volunteer (conference support)}
      {Dec.\ 2024}
      {Laboratory for Space Research, The University of Hong Kong (HKU); \'{E}cole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL)}

    \cvEvent
      {Celestial Holography Summer School 2024}
      {Participant}
      {Jul.\ 2024}
      {Perimeter Institute for Theoretical Physics}

    \cvEvent
      {International Symposium on Cosmology and Particle Astrophysics 2023 (CosPA 2023)}
      {Participant}
      {Nov.\ 2023}
      {Department of Physics and Institute of Theoretical Physics, The Chinese University of Hong Kong (CUHK)}

    \cvEvent
      {Multimessenger Astronomy: Bridging Transients, Lensing, and Dark Matter (Cosmic Frontiers)}
      {Participant}
      {Nov.\ 2023}
      {Department of Physics, CUHK}

  \resumeSubHeadingListEnd

%---------------------------------

%----------- AWARDS & HONORS -----------

%\section{Awards \& Honors}
  %\vspace{2pt}
  %\resumeSubHeadingListStart
    %\small{\item{

      % \textbf{<Award name>:}{ <Granting body/Institution>. <Brief qualifier: competitive/selected/nomination-based>. (<Mon.\ YYYY>) } \\ \vspace{3pt}

      % Example formats:
      % \textbf{Outstanding Graduate Scholarship:}{ Huazhong University of Science and Technology. Competitive; awarded to top-ranked graduate students. (Oct.\ 2025)} \\ \vspace{3pt}

      % If it is universal / non-competitive, either omit, or label clearly:
      % \textbf{Graduate Academic Scholarship:}{ Huazhong University of Science and Technology. Institutional scholarship (standard graduate support). (Sep.\ 2025 -- Present)} \\

    %}}
  %\resumeSubHeadingListEnd

%--------------------------------------%

%----------- PROFESSIONAL ACTIVITIES -----------

\section{Professional Activities}
  \vspace{2pt}
  \resumeSubHeadingListStart

\resumeSubheading
  {LISA (Laser Interferometer Space Antenna) Consortium}{}
  {Member}{Jan.\ 2026 \textbf{--} Present}

    \resumeSubheading
      {Laboratory for Space Research, The University of Hong Kong}{Hong Kong SAR, China}
      {Member}{Oct.\ 2023 \textbf{--} Nov.\ 2024}

    \resumeSubheading
      {Chinese Physical Society (CPS)}{}
      {Student Member}{May 2021 \textbf{--} Apr.\ 2022} % e.g., 2019 -- 2022
      
  \resumeSubHeadingListEnd
  %------------------------------------------

%----------- OUTREACH ACTIVITIES -----------

\section{Outreach Activities}
  \vspace{2pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {China Skywatcher Asteroid Search Campaign}{Jan.\ 2025 \textbf{--} Feb.\ 2025}
      {Participant}{International Astronomical Search Collaboration (IASC)}
    % \resumeItemListStart
    %   \resumeItem{(Optional) Performed image-based screening and candidate reporting as part of the campaign workflow.}
    % \resumeItemListEnd

  \resumeSubHeadingListEnd

\end{document}
% ---------- RESEARCH INTERESTS ----------
\section{Research Interests}
\vspace{2pt}
\resumeSubHeadingListStart
  \small{\item{Gravitational-wave astrophysics; space-based GW detection; compact binaries (double white dwarfs); Milky Way structure inference; time-series analysis.}}
\resumeSubHeadingListEnd

%----------- REFERENCES -----------%
\section{References}
  \vspace{2pt}
  References available upon request.
%----------------------------------------

    \textbf{\Huge \scshape Ruo-Yu Guan} \\[-2pt] \vspace{3pt}
    \small \textit{Research interests: gravitational-wave astrophysics; Galactic double white dwarfs; Milky Way structure; population inference} \\[4pt]
    \small